How unprecedented was the February 2021 Texas cold snap?

### 2021-02-28 doc/article.tex
Improve README

%\title[PREPRINT: Doss-Gollin, Farnham, Lall, and Modi]{How unprecedented was the February 2021 Texas cold snap?}
\title{How unprecedented was the February 2021 Texas cold snap?}

>>>>

\vspace*{1in}

{\LARGE How unprecedented was the February 2021 Texas cold snap?}

\vspace*{1in}

This is a non-peer reviewed preprint submitted to EarthArXiv by James Doss-Gollin, David J. Farnham, Upmanu Lall, and Vijay Modi.
This manuscript has been submitted to \emph{Environmental Research Letters}.
If accepted, a link to the published DOI will be provided here.

\clearpage

%\title[PREPRINT: Doss-Gollin, Farnham, Lall, and Modi]{How unprecedented was the February 2021 Texas cold snap?}
\title[PREPRINT by Doss-Gollin, Farnham, Modi, and Lall]{How unprecedented was the February 2021 Texas cold snap?}
